An Embedding Framework for the Design and Analysis of Consistent Polyhedral Surrogates

### 2022-06-02 poly-embed-journal/poly-embed-journal.tex
who knows, plus meeting notes

\section{General characteristics of polyhedra}
\label{app:polyhedra}
\subsection{Definitions and preliminaries}
\label{app:polyhedra:defs}
\begin{definition}[Closed halfspace]
  A closed halfspace is a set of the form $H_{(w,b)}^+ := \{ x \in \reals^d \mid \inprod{x}{w} \geq b\}$ for any $(w,b) \in \reals^d \times \reals$.
  % Similarly let $H_{(w,b)}^- := \{ x \in \reals^d \mid \inprod{x}{w} \leq b\}$.
\end{definition}
\begin{definition}[Hyperplane]
  A hyperplane is a set of the form $H_{(w,b)} := \{ x \in \reals^d \mid \inprod{x}{w} = b\}$ for any $(w,b)\in\reals^d \times \reals$.
  % The halfspaces corresponding to a hyperplane $H = H_{(w,b)}$ are the sets $H_{(w,b)}^+$ and $H_{(w,b)}^-$.
\end{definition} 
Observe that $H_{(w,b)} = \partial H^+_{(w,b)}$, meaning the hyperplane $H_{(w,b)}$ is the boundary of $H^+_{(w,b)}$.
Thus, for any halfspace $H^+$, we have that $H^+$ is one of the two halfspaces corresponding to the hyperplane $\partial H^+ = H$.

@@

	It is just left to show (iii).
	%Suppose for contradiction that there was a set of closed halfspaces $\H$ such that $P = \cap \H$, but there was a $H^+_{(w,b)} \in \H^* \setminus \H$, and therefore $\H^* \not \subseteq \H$.
	By (i), we know that each $H^+ \in \H^*$ uniquely determines a facet of $P$.
	Moreover, by (ii), define $F := P \cap H$, where $H = \partial H^+$ and $H^+ \in \H^*$, which is a facet of $P$ and of dimension $d-1$.
	The facet $F$ can then be defined by $d$ affinely independent points (contained in $P$), whose affine hull is $H$.
	As halfspaces are uniquely determined, so is the facet $F = P \cap H$.
	As polyhedron are uniquely determined by their facets (by Minkowski's uniqueness theorem, cf.,~\citep{klain2004minkowski}), we must have $H^+ \in \H^*$. 
	\jessiet{This is not as precise as I'd like... but also I think it follows more immediately from Minkowski's uniqueness theorem}

@@

\subsection{Notation}\label{appsubsec:notation}
Within this appendix, we use some self-contained notation.
We will later consider losses over a finite set of outcomes $\Y$; to make notation consistent, we use $\reals^\Y_+$ throughout as shorthand for $\reals^{|\Y|}_+$, and let $d := |\Y|+1$.

Fix a set $\V \subseteq \reals^\Y_+$, and consider the concave function $g_\V : x \mapsto \inf_{v \in \V}\inprod{v}{x} - \delta(x \mid \reals^\Y_+)$.
We denote the hypograph of $g_\V$ by $\hyp(g_\V) = \{(x,c) \mid c \leq g(x)\} \subseteq \reals^\Y_+ \times \reals$.

Given any $v \in \V \subseteq \reals^\Y_+$, define $H^+_v := H^+_{(v, -1)} = \{(x, c) \in \reals^{\Y}_+ \times \reals \mid \inprod{v}{x} = c\}$.
%, where $(v, -1)\in\reals^\Y_+\times\reals$ defines a halfspace.
Similarly, we denote $H_y^+ := H_{(e_y, 0)}^+$ for any $y \in \Y$; the latter will help us restrict a constructed polyhedron to the nonnegative orthant. 
Extending to hyperplanes, we construct $H_v := H_{(v,-1)}$ and observe that $H_v = \partial H^+_v$ for $v \in \reals^\Y_+$ and define $H_y := H_{(e_y, 0)}$ so that $H_y = \partial H^+_y$.
Given a polyhedron $P$, we denote the face $F^P_v := H_v \cap P$.
If $P$ is understood from context, we simply denote this face $F_v$.

Finally, given a set $\V \subseteq \reals^d$, we let $\H_{\V} = \{H_v^+ \mid v\in\V\}$ denote the set of halfspaces generated by $\V$, $\H_\Y = \{H_y^+ \mid y\in\Y\}$.
If $\V$ and $\Y$ are understood from context, we may denote $\H := \H_\V \cup\H_\Y$.

\subsection{Finitely generated polyhedra}\label{appsubsec:phase1}
Throughout, we will work with a (minimizable) function $g_\V$ generated by a set $\V \subseteq \reals^\Y_+$ of the following form.

\begin{definition}\label{def:g-finite}
  Given a set $\V \subseteq \reals^\Y_+$, define the function $g_\V : \reals_+^\Y \to \reals_+$ by
  \begin{align*}
    g_\V(x) = \inf_{v\in\V} \inprod{x}{v} - \delta(x \mid \reals_+^\Y)~. % = \min_{v\in\V} \inprod{x}{v} - \delta(x \mid \reals_+^\Y)~.~
  \end{align*}
\end{definition}

We first observe that the region generated by the intersection of the $H^+_y$ halfspaces restricts the hypograph of any $g_\V$ to be finite only on the nonnegative orthant.
\begin{lemma}\label{lem:x-nonneg-orthant-iff-intersection-HY}
  $\cap \H_\Y = \reals^\Y_+ \times \reals$.
\end{lemma}
\begin{proof}
  The result follows if we show $x \in \reals^\Y_+ \iff (x,c) \in \cap \H_\Y$ for all $c \in \reals$.

@@

>>>>

\section{General characteristics of polyhedra}
\label{app:polyhedra}
\subsection{General definitions for polyhedra}
\label{app:polyhedra:defs}
\begin{definition}[Closed halfspace]
  A closed halfspace is a set of the form $H_{(w,b)}^+ := \{ x \in \reals^d \mid \inprod{x}{w} \geq b\}$ for any $(w,b) \in \reals^d \times \reals$.
  % Similarly let $H_{(w,b)}^- := \{ x \in \reals^d \mid \inprod{x}{w} \leq b\}$.
\end{definition}
\begin{definition}[Hyperplane]
  A hyperplane is a set of the form $H_{(w,b)} := \{ x \in \reals^d \mid \inprod{x}{w} = b\}$ for any $(w,b)\in\reals^d \times \reals$.
  % The halfspaces corresponding to a hyperplane $H = H_{(w,b)}$ are the sets $H_{(w,b)}^+$ and $H_{(w,b)}^-$.
\end{definition} 
Observe that $H_{(w,b)} = \partial H^+_{(w,b)}$, meaning the hyperplane $H_{(w,b)}$ is the boundary of $H^+_{(w,b)}$.
Thus, for any halfspace $H^+$, we have that $H^+$ is one of the two halfspaces corresponding to the hyperplane $\partial H^+ = H$.

@@

	It is just left to show (iii).
  \raf{Let $\H$ be a finite set of closed halfspaces such that $P = \cap \H$.}
	%Suppose for contradiction that there was a set of closed halfspaces $\H$ such that $P = \cap \H$, but there was a $H^+_{(w,b)} \in \H^* \setminus \H$, and therefore $\H^* \not \subseteq \H$.
	By (i), we know that each $H^+ \in \H^*$ uniquely determines a facet of $P$.
	Moreover, by (ii), define $F := P \cap H$, where $H = \partial H^+$ and $H^+ \in \H^*$, which is a facet of $P$ and of dimension $d-1$.
	The facet $F$ can then be defined by $d$ affinely independent points (contained in $P$), whose affine hull is $H$.
	As halfspaces are uniquely determined, so is the facet $F = P \cap H$.
	As polyhedron are uniquely determined by their facets (by Minkowski's uniqueness theorem, cf.,~\citep{klain2004minkowski}), we must have $H^+ \in \H^*$. 
	\jessiet{This is not as precise as I'd like... but also I think it follows more immediately from Minkowski's uniqueness theorem}

@@

\subsection{Specializing to $\reals^\Y \times \reals$}\label{appsubsec:notation}
Within this appendix, we use some self-contained notation to work in the function graph space $\reals^\Y \times \reals$.
We will later consider losses over a finite set of outcomes $\Y$; to make notation consistent, we use $\reals^\Y_+$ throughout as shorthand for $\reals^{|\Y|}_+$, and let $d := |\Y|+1$.

Given any $v \in \reals^\Y_+$, define $H^+_v := H^+_{(v, -1)} = \{(x, c) \in \reals^{\Y}_+ \times \reals \mid \inprod{v}{x} = c\}$.
%, where $(v, -1)\in\reals^\Y_+\times\reals$ defines a halfspace.
Similarly, we denote $H_y^+ := H_{(e_y, 0)}^+$ for any $y \in \Y$; the latter will help us restrict a constructed polyhedron to the nonnegative orthant. 
Extending to hyperplanes, we construct $H_v := H_{(v,-1)}$ and observe that $H_v = \partial H^+_v$ for $v \in \reals^\Y_+$ and define $H_y := H_{(e_y, 0)}$ so that $H_y = \partial H^+_y$.

Given a set $\V \subseteq \reals^d$, we let $\H_{\V} = \{H_v^+ \mid v\in\V\}$ denote the set of halfspaces generated by $\V$, $\H_\Y = \{H_y^+ \mid y\in\Y\}$.
If $\V$ and $\Y$ are understood from context, we may denote $\H := \H_\V \cup\H_\Y$.

For any $S \subseteq \reals^k$, let $\delta(\cdot \mid S):\reals^k \to \reals \cup \{\infty\}$ be the convex indicator function, given by $\delta(x \mid S) = 0$ if $x\in S$ and $\infty$ otherwise.
Throughout, we will work with a function $g_\V$ generated by a set $\V \subseteq \reals^\Y_+$ of the following form.
Intuitively, one can think of $g_\V$ as a Bayes risk, where $\V$ is the report set, and the input acts like a label distribution.

\begin{definition}\label{def:g-finite}
  Given a set $\V \subseteq \reals^\Y_+$, define the function $g_\V : \reals_+^\Y \to \reals_+$ by
  \begin{align*}
    g_\V(x) = \inf_{v\in\V} \inprod{x}{v} - \delta(x \mid \reals_+^\Y)~. % = \min_{v\in\V} \inprod{x}{v} - \delta(x \mid \reals_+^\Y)~.~
  \end{align*}
\end{definition}
\noindent
We denote the hypograph of $g_\V$ by $\hyp(g_\V) = \{(x,c) \mid c \leq g(x)\} \subseteq \reals^\Y_+ \times \reals$.

A first observation is that the region generated by the intersection of the $H^+_y$ halfspaces restricts the hypograph of any $g_\V$ to be finite only on the nonnegative orthant.
\begin{lemma}\label{lem:x-nonneg-orthant-iff-intersection-HY}
  $\cap \H_\Y = \reals^\Y_+ \times \reals$.
\end{lemma}
\begin{proof}
  The result follows if we show $x \in \reals^\Y_+ \iff (x,c) \in \cap \H_\Y$ for all $c \in \reals$.

@@

\raf{Given a polyhedron $P$, we denote the face $F^P_v := H_v \cap P$.
If $P$ is understood from context, we simply denote this face $F_v$.}
